### 2023-02-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@d0abb50158ae5e1a5c104ffcbbf979a0b5a01093 🚀

However, representing species interactions probabilistically can also be
challenging. Beyond methodological difficulties in estimating these
numbers, there are important conceptual challenges in defining what we
mean by ``probability of interactions.'' To the best of our knowledge,
because the building blocks of this mathematical representation of food
webs are still being laid, there is no clear definition found in the
literature. This is worrisome, since working with probabilistic species
interactions without clear guidelines could be misleading as much for
field ecologists as for computational ecologists who use and generate
these data. In this contribution, we outline different ways to define
and interpret interactions probabilities in network ecology and propose
an approach to thinking about them. These definitions mostly depend on
the study system (e.g.~local network or metaweb) and on the method used
to generate them. We show that different definitions can have different
ecological implications, especially regarding spatial, temporal, and
taxonomic scaling. Although we will focus on food webs, our observations
and advice can be applied to all types of ecological networks, from
plant-pollinator to host-parasite networks. Specifically, we argue that
probabilities should be better documented, defined mathematically, and
used with caution when describing species interactions.

@@

The basic unit of food webs and other ecological networks are
individuals that interact with each others (e.g., by predation; Elton
2001), forming individual-based networks. The aggregation of these
individuals into more or less homogeneous groups (e.g., populations,
species, trophic species, families) allows us to represent networks at
broader scales, which impacts the properties and behaviour of these
systems (Guimarães 2020). A network's nodes can thus designate distinct
levels of organization, whereas the edges linking these nodes can
describe a variety of interaction measures. When using a Boolean
(yes-no) representation of biotic interactions, the observation that one
individual from group (or node) \(i\) interacts with another individual
from group \(j\) is enough to set the interaction \(A_{i,j}\) to 1. This
simplified representation of food webs is a highly valuable source of
ecological information (Pascual \emph{et al.} 2006) even though it
overlooks important factors regarding interaction strengths. These, in
turn, can be represented using weighted interactions, which better
describe the energy flows, demographic impacts or frequencies of
interactions between nodes (Berlow \emph{et al.} 2004; Borrett \&
Scharler 2019), with \(A_{i,j} \in \mathbb{N}\) or \(\mathbb{R}\)
depending on the measure. For example, they can be used to estimate the
average number of prey individuals consumed by the predators in a given
time period. This extra amount of ecological information typically comes
at a cost of greater sampling effort or data requirement in predictive
models (Strydom \emph{et al.} 2021), which can lead to high
uncertainties when building these types of networks. Therefore,
important methodological and conceptual decisions must be made when
sampling and building food webs.

The uncertainty and spatiotemporal variability of both types of trophic
interactions (Boolean and weighted) can be represented
probabilistically. On one hand, Boolean interactions follow a Bernoulli
distribution \(A_{i,j} \sim {\rm Bernoulli}(p)\), with \(p\) being the
probability of interactions. The only two possible outcomes are the
presence (\(A_{i,j} = 1\)) or absence (\(A_{i,j} = 0\)) of an
interaction between the two nodes. Weighted interactions, on the other
hand, can follow various probability distributions depending on the
measure used. In this case, the event's outcome is the value of
interaction strength. For instance, weights can follow a Poisson
distribution \(A_{i,j} \sim {\rm Poisson}(\lambda)\) when predicting
frequencies of interactions between pairs of nodes, with \(\lambda\)
being the expected rate of interaction. The definition and
interpretation of parameters like \(p\) and \(\lambda\) are inextricably
linked to environmental and biological factors such as species relative
abundance, traits, area, and time, depending on the type of interaction.
Because Boolean species interactions are much more documented in the
literature, our primary focus in this contribution will be on addressing
the challenges in defining and interpretating \(p\) for pairwise species
interactions.

@@

Metawebs are networks of potential interactions, representing the
probability that two taxa can interact regardless of biological
plasticity, environmental variability or co-occurrence. They are the
network analogue to the species pool, where local networks originate
from a subset of both species (nodes) and interactions (edges). For this
reason, they have been initially designed for broad spatial, temporal,
and taxonomic scales (e.g, species food webs at the continental scale).
However, in the next section, we argue that this concept can also be
used at smaller scales, with similar ecological meaning.

@@

As opposed to metawebs, probabilistic local food webs represent the
likelihood that two species will interact at a specific location and
within a given time period; in other words, they are context dependant.
To be specific, space is defined here as the geographic coordinates
\((x, y)\) of the spatial boundaries delineating the system, whereas
time is the time interval \(t\) during which interactions were sampled
or for which they were predicted. We want to point out that they are not
single values, but rather continued dimensions that could be outlined
differently depending on the study system. Regardless of how they were
defined, they always delineate a specific area \(A\) and duration \(t\).
These could refer to the sampled area and duration or to the targeted
location and time period.

Many factors could be taken into consideration when estimating the
probability that a predator species \(i\) interacts with a given prey
species \(j\) locally. One of the most important is species
co-occurrence \(C\), which is a Boolean describing if both species can
be found at location and time (\(x\), \(y\), \(t\)). Surely, the
probability that the interaction is realized must be \(0\) when species
do not co-occur (\(C = 0\)). Interaction probabilities can also be
conditional on other biological and environmental variables, such as
temperature, precipitation, presence of shelters, phenotypic plasticity,
phenology, and presence of other interacting species in the network.
These conditions can affect species traits, which greatly impact the
capacity of species to interact (Poisot \emph{et al.} 2015). Similarly,
species relative abundance is another important predictor of the
probability of interaction, because it impacts the probability that
species will randomly encounter (Canard \emph{et al.} 2012; Canard
\emph{et al.} 2014; Poisot \emph{et al.} 2015). Here, we will use the
variable \(\Omega\) as a substitute for the biological and ecological
context in which interaction probabilities were estimated. This gives us
the following equation for the probability of realized interaction
between species (or taxa) \(i\) and \(j\) in a local network \(N\):

@@

which can be read as the probability of local interaction between the
two species in an area \(A\) and time interval \(t\), given their
co-occurrence \(C\) and specific environmental and biological conditions
\(\Omega\).

@@

\hypertarget{from-potential-to-realized-interactions}{%
\subsection{From potential to realized
interactions}\label{from-potential-to-realized-interactions}}

@@

\hypertarget{scaling}{%
\section{Scaling}\label{scaling}}

\hypertarget{spatial-and-temporal-scales}{%
\subsection{Spatial and temporal
scales}\label{spatial-and-temporal-scales}}

Metawebs and local networks intrinsically differ in their relation to
scale. On one hand, as mentioned above, probabilistic metawebs are
context independent, i.e., probabilistic pairwise interactions do not
scale with space and time because they depend solely on the biological
capacity of the two taxa to interact. This implies that the estimated
likelihood that two species can potentially interact should be the same
among all metawebs in which they are present. In practice, this is
rarely the case because ecologists use different methods and data to
estimate these probabilities of interactions. However, in the case where
local metawebs \(M_{x,y}\) are subsampled from their regional
counterpart \(M_0\), we should expect edge values to be identical among
all networks, regardless of their spatial scale,
i.e.~\(P_{M_{x,y}}(i \rightarrow j) = P_{M_0}(i \rightarrow j)\). On the
other hand, local probabilistic networks are indissociable from their
spatial and temporal contexts because there are more opportunities of
interactions (e.g., more individuals, more trait variations, more chance
of encounter) in a larger area and longer time period (McLeod \emph{et
al.} 2020). Let \(N_0\) be a local probabilistic food web delineated in
an area \(A_0\) and \(N_1\) a network of area \(A_1 < A_0\) within
\(A_0\). We should expect the probability that \(i\) and \(j\) interacts
to scale spatially, i.e.
\(P_{N_1}(i \rightarrow j | A < A_0) \le P_{N_0}(i \rightarrow j | A = A_0)\).
Similarly, the temporal scaling of probabilistic local food webs could
be manifested through the effect of sampling effort on the observation
of interactions (Jordano 2016; McLeod \emph{et al.} 2021) or of time
itself on their realization (Poisot \emph{et al.} 2012). There are many
network-area relationships (e.g., Wood \emph{et al.} 2015; Galiana
\emph{et al.} 2018) and interaction accumulation curves (e.g, Jordano
2016) explored in the literature. These could inspire the development
and testing of different equations describing the spatiotemporal scaling
of probabilistic pairwise interactions in local networks, which are over
the scope of this manuscript.

@@

\begin{itemize}
\tightlist
\item
  Making interaction probabilities spatiotemporally explicit
\end{itemize}

@@

\hypertarget{taxonomic-scale}{%
\subsection{Taxonomic scale}\label{taxonomic-scale}}

@@

\begin{itemize}
\tightlist
\item
  There are different biological interpretations of probabilities in
  food webs at the individual level and at higher taxonomic levels.
\item
  How does the scaling up of the nodes from an individual to population
  to any higher taxonomic group change our interpretation of interaction
  probabilities? How does the aggregation change our interpretation?
\item
  How is it similar and different to spatial and temporal scaling?
  Basically, all kinds of scaling are just different ways to aggregate
  individuals or nodes.
\end{itemize}

@@

The emergence of probabilistic thinking in network ecology has paved the
way to a better assessment of the spatiotemporal variability and
uncertainty of biotic interactions. However, we showed that network
metadata are perhaps as important as interaction data themselves when it
comes to interpreting probabilistic food webs in ecological terms.
First, the type of probabilistic interaction (potential or realized)
impacts the importance of scale, with interactions in metawebs being
scale independent, both spatially and temporally. Second, the conditions
in which local networks were estimated (e.g., area, time, biological and
environmental factors) and the attributes of the interacting species
that were considered (e.g., species co-occurrence) are essential
contextual factors that impact the mathematical representation of
probabilities and their resulting behaviour. Third, the biological
interpretation of probabilities changes with the level of organization
of the network due to the aggregation of individuals into broader
groups. All these information should be available as clear metadata so
that ecologists can use probabilistic network data appropriately.

@@

@@

@@

@@

>>>>

However, representing species interactions probabilistically can also be
challenging. Beyond methodological difficulties in estimating these
numbers, there are important conceptual challenges in defining what we
mean by ``probability of interactions.'' To the best of our knowledge,
because the building blocks of this mathematical representation of food
webs are still being laid, there is no clear definition found in the
literature or data standard when it comes to publishing data on
probabilistic interactions (see Salim \emph{et al.} 2022 for a
discussion on data standardization for mutualistic networks). This is
worrisome, since working with probabilistic species interactions without
clear guidelines could be misleading as much for field ecologists as for
computational ecologists who use and generate these data. In this
contribution, we outline different ways to define and interpret
interactions probabilities in network ecology and propose an approach to
thinking about them. These definitions mostly depend on the study system
(e.g.~local network or metaweb) and on the method used to generate them.
We show that different definitions can have different ecological
implications, especially regarding spatial, temporal, and taxonomic
scaling. Although we will focus on food webs, our observations and
advice can be applied to all types of ecological networks, from
plant-pollinator to host-parasite networks. Indeed, all ecological
networks, whether they are unipartite or bipartite, share fundamental
commonalities in their biological conceptualization and mathematical
representation that support these comparisons (i.e., they all describe
groups of individuals interacting with each other). Regardless of the
study system, we argue that probabilities should be better documented,
defined mathematically, and used with caution when describing species
interactions.

@@

The basic unit of food webs and other ecological networks are
individuals that interact with each others (e.g., by predation; Elton
2001), forming individual-based networks. The aggregation of these
individuals into more or less homogeneous groups (e.g., populations,
species, trophic species, families) allows us to represent networks at
broader scales, which impacts the properties and behaviour of these
systems (Guimarães 2020). A network's nodes can thus designate distinct
levels of organization, whereas the edges linking these nodes can
describe a variety of interaction measures. When using a Boolean
(yes-no) representation of biotic interactions, the observation that one
individual from group (or node) \(i\) interacts with another individual
from group \(j\) is enough to set the interaction \(A_{i,j}\) to 1. This
simplified representation of food webs is a highly valuable source of
ecological information (Pascual \emph{et al.} 2006) even though it
overlooks important factors regarding interaction strengths. These, in
turn, can be represented using weighted interactions, which better
describe the energy flows, demographic impacts or frequencies of
interactions between nodes (Berlow \emph{et al.} 2004; Borrett \&
Scharler 2019), with \(A_{i,j} \in \mathbb{N}\) or \(\mathbb{R}\)
depending on the measure. For example, they can be used to estimate the
average number of prey individuals consumed by the predators in a given
time period (e.g., the average number of fish in the stomach of a
piscivorous species). Interaction strengths can also be used as good
estimators of the parameters describing species interactions in a
Lotka-Volterra model (e.g., Emmerson \& Raffaelli 2004). This extra
amount of ecological information typically comes at a cost of greater
sampling effort or data requirement in predictive models (Strydom
\emph{et al.} 2021), which can lead to high uncertainties when building
these types of networks. Therefore, important methodological and
conceptual decisions must be made when sampling and building food webs.

The uncertainty and spatiotemporal variability of both types of trophic
interactions (Boolean and weighted) can be represented
probabilistically. On one hand, Boolean interactions follow a Bernoulli
distribution \(A_{i,j} \sim {\rm Bernoulli}(p)\), with \(p\) being the
probability of interactions. The only two possible outcomes are the
presence (\(A_{i,j} = 1\)) or absence (\(A_{i,j} = 0\)) of an
interaction between the two nodes. Weighted interactions, on the other
hand, can follow various probability distributions depending on the
measure used. In this case, the event's outcome is the value of
interaction strength. For instance, weights can follow a Poisson
distribution \(A_{i,j} \sim {\rm Poisson}(\lambda)\) when predicting
frequencies of interactions between pairs of nodes, with \(\lambda\)
being the expected rate of interaction. Note that weighted interactions
can be converted to probabilistic interactions by normalizing. The
definition and interpretation of parameters like \(p\) and \(\lambda\)
are inextricably linked to environmental and biological factors such as
species relative abundance, traits, area, and time, depending on the
type of interaction.\\
Because Boolean species interactions are much more documented in the
literature, our primary focus in this contribution will be on addressing
the challenges in defining and interpretating \(p\) for pairwise species
interactions.

@@

Metawebs are networks of potential interactions, representing the
probability that two taxa can interact regardless of biological
plasticity, environmental variability or co-occurrence. Instead of
describing stochastic biological processes occurring in nature,
probabilistic potential interactions can be thought of as a measure of
imperfect knowledge about the capacity of two taxa to interact. They are
the network analogue to the species pool, where local networks originate
from a subset of both species (nodes) and interactions (edges). For this
reason, they have been initially designed for broad spatial, temporal,
and taxonomic scales (e.g, species food webs at the continental scale).
However, in the next section, we argue that this concept can also be
used at smaller scales, with similar ecological meaning.

@@

As opposed to metawebs, probabilistic local food webs represent the
likelihood that two species will interact at a specific location and
within a given time period; in other words, they are context dependant.
They could also represent the likelihood of observing these interactions
within a given area and time. To be specific, space is defined here as
the geographic coordinates \((x, y)\) of the spatial boundaries
delineating the system, whereas time is the time interval \(t\) during
which interactions were sampled or for which they were predicted. We
want to point out that they are not single values, but rather continued
dimensions that could be outlined differently depending on the study
system. Regardless of how they were defined, they always delineate a
specific area \(A\) and duration \(t\). These could refer to the sampled
area and duration or to the targeted location and time period.

Many factors could be taken into consideration when estimating the
probability that a predator species \(i\) interacts with a given prey
species \(j\) locally. One of the most important is species
co-occurrence \(C\), which is a Boolean describing if both species can
be found at location and time (\(x\), \(y\), \(t\)). Surely, the
probability that the interaction is realized must be \(0\) when species
do not co-occur (\(C = 0\)). Interaction probabilities can also be
conditional on other biological and environmental variables, such as
temperature, precipitation, presence of shelters, phenotypic plasticity,
phenology, and presence of other interacting species in the network.
These conditions can affect species traits, which greatly impact the
capacity of species to interact (Poisot \emph{et al.} 2015). Similarly,
species relative abundance is another important predictor of the
probability of interaction, because it impacts the probability that
species will randomly encounter (Canard \emph{et al.} 2012; Canard
\emph{et al.} 2014; Poisot \emph{et al.} 2015). Here, we will use the
variable \(\Omega\) as a substitute for the biological and ecological
context in which interaction probabilities were estimated, including the
presence of higher-order interactions. This gives us the following
equation for the probability of realized interaction between species (or
taxa) \(i\) and \(j\) in a local network \(N\):

@@

which can be read as the probability of local interaction between the
two species in an area \(A\) and time interval \(t\), given their
co-occurrence \(C\) and specific environmental and biological conditions
\(\Omega\). These conditions do not systematically need to be specified
for all studies. However, when they are, they should be made explicit in
the metadada.

@@

\hypertarget{applications-of-probabilistic-interactions-data}{%
\section{Applications of probabilistic interactions
data}\label{applications-of-probabilistic-interactions-data}}

\hypertarget{inferring-probabilistic-local-food-webs-from-metawebs}{%
\subsection{Inferring probabilistic local food webs from
metawebs}\label{inferring-probabilistic-local-food-webs-from-metawebs}}

@@

\hypertarget{sampling-random-draws-from-probabilistic-food-webs}{%
\subsection{Sampling random draws from probabilistic food
webs}\label{sampling-random-draws-from-probabilistic-food-webs}}

@@

\hypertarget{describing-the-spatial-and-temporal-scaling-of-probabilistic-interactions}{%
\subsection{Describing the spatial and temporal scaling of probabilistic
interactions}\label{describing-the-spatial-and-temporal-scaling-of-probabilistic-interactions}}

Metawebs and local networks intrinsically differ in their relation to
scale. On one hand, as mentioned above, probabilistic metawebs are
context independent, i.e., probabilistic pairwise interactions do not
scale with space and time because they depend solely on the biological
capacity of the two taxa to interact. This implies that the estimated
likelihood that two species can potentially interact should be the same
among all metawebs in which they are present. In practice, this is
rarely the case because ecologists use different methods and data to
estimate these probabilities of interactions (e.g., different sampling
area and time period). However, in the case where local metawebs
\(M_{x,y}\) are subsampled from their regional counterpart \(M_0\), we
should expect edge values to be identical among all networks, regardless
of their spatial scale,
i.e.~\(P_{M_{x,y}}(i \rightarrow j) = P_{M_0}(i \rightarrow j)\). On the
other hand, local probabilistic networks are indissociable from their
spatial and temporal contexts because there are more opportunities of
interactions (e.g., more individuals, more trait variations, more chance
of encounter) in a larger area and longer time period (McLeod \emph{et
al.} 2020). Let \(N_0\) be a local probabilistic food web delineated in
an area \(A_0\) and \(N_1\) a network of area \(A_1 < A_0\) within
\(A_0\). We should expect the probability that \(i\) and \(j\) interacts
to scale spatially,
i.e.~\(P_{N_1}(i \rightarrow j | A < A_0) \le P_{N_0}(i \rightarrow j | A = A_0)\).
Similarly, the temporal scaling of probabilistic local food webs could
be manifested through the effect of sampling effort on the observation
of interactions (Jordano 2016; McLeod \emph{et al.} 2021) or of time
itself on their realization (Poisot \emph{et al.} 2012). There are many
network-area relationships (e.g., Wood \emph{et al.} 2015; Galiana
\emph{et al.} 2018) and interaction accumulation curves (e.g, Jordano
2016) explored in the literature. These could inspire the development
and testing of different equations describing the spatiotemporal scaling
of probabilistic pairwise interactions in local networks, which are over
the scope of this manuscript.

@@

\hypertarget{making-probabilistic-interactions-spatiotemporally-explicit}{%
\subsection{Making probabilistic interactions spatiotemporally
explicit}\label{making-probabilistic-interactions-spatiotemporally-explicit}}

The variability of species interactions spurred the development of
methods aiming at predicting ecological networks at fine spatial and
temporal scales. For example, Bohan \emph{et al.} (2017) proposed a
framework to reconstruct networks in real time using continuous
biomonitoring. Here, we will build on these studies by proposing a
simple model to make probabilistic local networks spatiotemporally
explicit. These types of models could prove useful when inferring food
webs across time and space from sparse data. However, they are not
suitable for metawebs, which are static objects.

One way that probabilistic food webs can be made spatiotemporally
explicit is by modelling interactions between co-occurring species as a
Poisson process with rate \(\lambda\). Specifically, if the total
observation time for a location is \(t_0\), the probability that two
co-occurring species \(i\) and \(j\) will interact during this time
period is
\(P_N(i \rightarrow j | C_{i,j} = 1, t = t_0) = 1-e^{-\lambda t_0}\),
which approaches \(1\) when \(t \to \infty\). The value of the parameter
\(\lambda\) could be estimated using prior data on interaction
strengths, if available. Additionally, we can estimate the probability
of co-occurrence at location \((x,y)\) with
\(P_{x,y}(C_{i,j} = 1) = P_{x,y}(i) P_{x,y}(j)\gamma\), where
\(P_{x,y}(i)\) and \(P_{x,y}(j)\) are respectively the probabilities of
occurrence of species \(i\) and \(j\) and \(\gamma\) is the strength of
association between occurrence and co-occurrence, as defined in Cazelles
\emph{et al.} (2016). Note that in empirical networks, \(\gamma\) is
typically \(> 1\) (Catchen \emph{et al.} 2023). The observation of this
interaction would thus follow a Bernoulli distribution with parameter
\(p = p_A(x,y)p_B(x,y)\gamma(1-e^{-\lambda t_0})\). This simple model
could be customized in many ways, e.g.~by linking \(\lambda\) with given
environmental variables or by adding in observation errors (i.e.,
probability of false negatives and false positives; Catchen \emph{et
al.} (2023)).

\hypertarget{exploring-different-levels-of-organization}{%
\subsection{Exploring different levels of
organization}\label{exploring-different-levels-of-organization}}

@@

\begin{itemize}
\tightlist
\item
  There are different biological interpretations of probabilities in
  food webs at the individual level and at higher taxonomic levels.
\item
  How does the scaling up of the nodes from an individual to population
  to any higher taxonomic group change our interpretation of interaction
  probabilities? How does the aggregation change our interpretation?
\item
  Why would we want to scale networks taxonomically?
\item
  Do all nodes need to be the same taxonomic scale, within a network?
\item
  How is it similar and different to spatial and temporal scaling?
  Basically, all kinds of scaling are just different ways to aggregate
  individuals or nodes.
\item
  Papers: Vázquez \emph{et al.} (2022)
\end{itemize}

@@

The emergence of probabilistic thinking in network ecology has paved the
way to a better assessment of the spatiotemporal variability and
uncertainty of biotic interactions. However, measuring probabilities
empirically can be strenuous given the difficulties of deciphering
species and interactions (Pringle \& Hutchinson 2020). In this context,
the development of computational methods makes it possible to estimate
interaction probabilities at large scales, which in turn can pinpoint
where we should go to optimise our sampling effort for better resolving
local food webs.

In this contribution, we showed that network metadata are perhaps as
important as interaction data themselves when it comes to interpreting
probabilistic food webs in ecological terms. First, the type of
probabilistic interaction (potential or realized) impacts the importance
of scale, with interactions in metawebs being scale independent, both
spatially and temporally. Second, the conditions in which local networks
were estimated (e.g., area, time, biological and environmental factors)
and the attributes of the interacting species that were considered
(e.g., species co-occurrence) are essential contextual factors that
impact the mathematical representation of probabilities and their
resulting behaviour. Third, the biological interpretation of
probabilities changes with the level of organization of the network due
to the aggregation of individuals into broader groups. All these
information should be available as clear metadata so that ecologists can
use probabilistic network data appropriately.

@@

\leavevmode\hypertarget{ref-Bohan2017NexGlo}{}%
Bohan, D.A., Vacher, C., Tamaddoni-Nezhad, A., Raybould, A., Dumbrell,
A.J. \& Woodward, G. (2017). Next-Generation Global Biomonitoring:
Large-scale, Automated Reconstruction of Ecological Networks.
\emph{Trends in Ecology \& Evolution}, 32, 477--487.

@@

\leavevmode\hypertarget{ref-Emmerson2004PrePre}{}%
Emmerson, M.C. \& Raffaelli, D. (2004). Predatorprey body size,
interaction strength and the stability of a real food web. \emph{Journal
of Animal Ecology}, 73, 399--409.

@@

\leavevmode\hypertarget{ref-Salim2022DatSta}{}%
Salim, J.A., Saraiva, A.M., Zermoglio, P.F., Agostini, K., Wolowski, M.,
Drucker, D.P., \emph{et al.} (2022). Data standardization of
plantpollinator interactions. \emph{GigaScience}, 11, giac043.

@@

\leavevmode\hypertarget{ref-VazquezSS2022EcoInt}{}%
Vázquez, D.P., Peralta, G., Cagnolo, L., Santos, M. \& Igual, E. autores
contribuyeron por. (2022). Ecological interaction networks. What we
know, what we don't, and why it matters. \emph{Ecología Austral}, 32,
670--697.
